\bfseries Equivariant convolution-based functions on tensor fields

### 2022-07-27 paper/cosmology.tex

% To-Do list:
% -----------
% - What are our GOALS!!?
%   -- one option: this formulation can express all equivariant differential operators discretized to a cubical d-torus. 
%   -- another option: can we produce a characterization of all equivariant functions (maybe based on invariants or these filters) that don't require the use of non-linearities.
%   -- another option: emulate cosmological simulations.
% - change N to N^3 in the appropriate locations; already done??
% - Understand what functions can and cannot be expressed on this model 
% - Extend it to non-linear maps (eg, by multiplications and contractions)
% - Should we be representing images in fourier space? Ask Leslie!
% - Understand the literature
%   -- Discretized vector calculus and differential geometry.
%   -- Group-equivariant CNNs; what's been done?
%   -- Understand how this formulation compares with steerable CNNs
%   -- What is known about what functions CNNs can represent? Ask Joan!
%  -- Define "local" functions

@@

% typesetting adjustments
\makeatletter
\renewcommand\section{\@startsection {section}{1}{\z@}%
  {-3.25ex \@plus -1ex \@minus -.2ex}%
  {1.5ex \@plus .2ex}%
  {\raggedright\normalfont\large\bfseries}}
\makeatother
\setlength{\textwidth}{5.00in}
\setlength{\oddsidemargin}{3.25in}
\addtolength{\oddsidemargin}{-0.5\textwidth}
\setlength{\textheight}{9.40in}
\setlength{\topmargin}{-0.50in}
\setlength{\footskip}{0.25in}
\pagestyle{myheadings}
\markboth{foo}{Hogg \& Villar / Emulating n-body simulations with equivariant CNNs}
\newcommand{\figurerule}{\rule[1ex]{\textwidth}{0.2pt}}
\linespread{1.08}
\frenchspacing\sloppy\sloppypar\raggedbottom

\title{\bfseries%
Equivariant convolution-based functions
of images or lattices
containing scalars, vectors, and tensors}
\author{Hogg, Villar, Blum-Smith, others}
\date{2022 June}

@@

\paragraph{Abstract:} HERE IS OUR ABSTRACT.

@@

\begin{definition}[Group $B_d$ of symmetries of a $d$- hypercube]
We denote by $B_d$ the group of rotation and reflection symmetries of the $d$-dimensional hypercube.
\end{definition}

>>>>

% To-Do list:
% -----------
% - What are our GOALS!!?
%   -- one option: this formulation can express all equivariant differential operators discretized to a cubical d-torus. 
%   -- another option: can we produce a characterization of all equivariant functions (maybe based on invariants or these filters) that don't require the use of non-linearities.
%   -- another option: emulate cosmological simulations.
% - change N to N^3 in the appropriate locations; already done??
% - Understand what functions can and cannot be expressed on this model 
% - Extend it to non-linear maps (eg, by multiplications and contractions)
% - Should we be representing images in fourier space? Ask Leslie!
% - Understand the literature
%   -- Discretized vector calculus and differential geometry.
%   -- Group-equivariant CNNs; what's been done?
%   -- Understand how this formulation compares with steerable CNNs
%   -- What is known about what functions CNNs can represent? all linear translation equivariant functions can be written as convvolutions if the filters are as large as the image (simple observation)
% what about non-linear? is there a polynomial basis here? 
%  -- Define "local" functions, is there a characterization of functions that can be written as convolutions with small filters?

@@

% typesetting adjustments
\makeatletter
\renewcommand\section{\@startsection {section}{1}{\z@}%
  {-3.25ex \@plus -1ex \@minus -.2ex}%
  {1.5ex \@plus .2ex}%
  {\raggedright\normalfont\large\bfseries}}
\makeatother
\setlength{\textwidth}{5.00in}
\setlength{\oddsidemargin}{3.25in}
\addtolength{\oddsidemargin}{-0.5\textwidth}
\setlength{\textheight}{9.40in}
\setlength{\topmargin}{-0.50in}
\setlength{\footskip}{0.25in}
\pagestyle{myheadings}
\markboth{foo}{Hogg \& Villar /Geometric filters for geometric images}
\newcommand{\figurerule}{\rule[1ex]{\textwidth}{0.2pt}}
\linespread{1.08}
\frenchspacing\sloppy\sloppypar\raggedbottom

\title{\bfseries%
Equivariant convolution-based functions
on tensor fields}
\author{Hogg, Villar, Blum-Smith, others}
\date{2022 June}

@@

\paragraph{Abstract:} We provide a construction for general equivariant convolution-based functions of images or lattices
containing scalars, vectors, and tensors. The formulation, inspired by Einstein summation notation, does not use point-wise activation functions, but it can universally approximate all analytic equivariant functions with respect to discrete rotations of the image. CHECK WITH BEN

@@

\begin{definition}[Group $B_d$ of symmetries of a $d$-hypercube]
We denote by $B_d$ the group of rotation and reflection symmetries of the $d$-dimensional hypercube.
\end{definition}
